---
title: "Arkansas Razorbacks Men's Basketball 2022-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::install_github("lbenz730/ncaahoopR")

library(ncaahoopR)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(ggthemes)
library(ggrepel)
library(gganimate)
library(ggforce)
library(ggtext)
library(ggalt)
library(ggsci)
library(ggpubr)
library(ggbeeswarm)
```

# Data

```{r, echo=FALSE}
ark_pbp <- get_pbp("Arkansas", "2022-23")
ark_roster <- get_roster("Arkansas", "2022-23")
ark_schedule <- get_schedule("Arkansas", "2022-23")
ark_season_box <- season_boxscore("Arkansas", "2022-23", aggregate = "average")
```

# Visualizations

## Circle Assist Network

A circle assist network in R is a function that creates a circular plot of how players on a basketball team assist each other for scoring points. Here, we are doing this for the entire 2022-23 Arkansas basketball season. Additionally, we can highlight a specific player if desired which in this case is Anthony Black, the starting PG for the Razorbacks this year.

```{r}
circle_assist_net("Arkansas", "2022-23", highlight_player = "Anthony Black", highlight_color = "#9D2235", three_weights = T, 
threshold = 0.1, message = NA, return_stats = T)
```
